A Large-Scale Study of the Use of Eval in R

### 2020-08-25 inst/paper/main.tex
Provenance: parse and metaprogramming

\input{tag/counts.tex}
\input{tag/corpus.tex}

@@

Here we talk about where the input of an eval comes from

@@

We look at how \emph{polymorphic} the \c{expr} argument of \eval can be, \ie
how many different types of the resolved \c{expr} there are per call sites,
in Figure~\ref{fig:polymorphism}. \DegreeMonomorphism of the call sites are
\emph{monomorphic}.

>>>>

\input{tag/counts.tex}
\input{tag/corpus.tex}
\input{tag/analysisStable.tex}

@@

Here we talk about where the input of an eval comes from.

Although \c{eval} takes an R expression, it can evaluate a string if this string is first parsed with \c{parse}, \c{str2expression} or \c{str2lang}. This happens for \PercentParsedEvals of the eval calls, and \PercentParsedCallSites of the call sites.

This corresponds to strings loaded from a file or to metaprogramming, \ie building new variables or functions by concatenating strings together. To detect this kind of metaprogramming, we look at the usage of the main concatenating functions in R, \c{paste}, \c{paste0} and \c{str_c}, and \PasteParsedEvals of the evals and \PasteParsedCallSite of the call sites using a parse function actually call a concatenating function.

@@

We look at how \emph{polymorphic} the \c{expr} argument of \eval can be, \ie
how many different types of the resolved \c{expr} there are per call sites,
in Figure~\ref{fig:polymorphism}. \PercentMonomorphic of the call sites are
\emph{monomorphic}.
